\section{Purpose}
\label{sec:purpose}
This paper is motivated by our experience of developing a metadata private messaging (MPM) software called Anysphere. In our whitepaper \cite[Section 3]{whitepaper}, we describe Anysphere's threat model and core protocol at a high level. This document aims to rigorously show that Anysphere's core protocol satisfies the metadata privacy we promise. 

Existing security proofs of MPMs (such as \cite{corrigan2010dissent, corrigan2015riposte, angel2016unobservable, ahmad2021addra}) have shown the privacy of a private information retrieval (PIR) system where users can deposit and retrieve information without revealing metadata to the server. We find these proofs unsatisfying for several reasons.
\begin{itemize}
    \item The security of the PIR system does not guarantee the security of the messaging system as a whole. A well-known example illustrating this is the Compromised Friend (CF) attack proposed by Angel, Lazar and Tzialla (\cite{angel2018cf}). They show that if an honest user makes friend with a malicious user, then the metadata of conversations between honest users might be compromised even with a secure PIR system. To our knowledge, no proofs exist that show immunity against CF attacks\footnote{Pung's security proof \cite{angel2018thesis} assumes honest users only ever talk to honest users.}. 
    
    We found a more powerful CF attack, described in \cref{sec:security-vulnerable}, as we write this paper. This vulnerability affects existing implementations of Pung and Addra, and can result in full compromise of metadata (timing, sender and receiver of PIR queries). This attack demonstrates that CF attacks can potentially cause more damage than expected in \cite{angel2018cf}. In light of this attack, we wish to rigorously prove that our MPM system can defend against CF attacks.
    
    \item Anysphere is based on Addra \cite{ahmad2021addra}. Addra is originally designed for users to hold exactly one conversation at a time. In our application, clients may hold many different conversations at the same time. We need to ensure that our adaptation does not introduce new vulnerabilities.
    
    \item Addra and Pung \cite{angel2016unobservable} assume that clients run in synchronous round, and each client sends exactly one message to the server each round. As clients have different level of resources, running synchronous rounds is not economical. For example, corporate users might wish rounds run faster to receive timely updates, while individual users might not want to participate in each round to preserve bandwidth. Anysphere uses asynchronous rounds where each client can transmit on a different schedule. We need to justify the security of this decision.
    
    \item The MPM systems mentioned above lack a mechanism to detect and retransmit lost or shuffled packages. We introduce an ACK mechanism in Anysphere to fix this issue. Justifying the security of this mechanism is nontrivial.
\end{itemize}

The paper is organized as follows. In \cref{sec:general-defn}, we present a formal security definition of what it means for a whole messaging system to be correct and secure under our threat model outlined in \cite{whitepaper}. In \cref{sec:security-vulnerable}, we describe the new CF attack, which we name the PIR Replay Attack. In \cref{sec:asphr-defn}, we describe a modified Anysphere core protocol in pseudocode. In \cref{sec:proofs} we prove that the protocol defined in \cref{sec:asphr-defn} satisfies the security definition in \cref{sec:general-defn}. A technical detail in the proof is delayed to \cref{sec:IND-CCPKA}. In \cref{sec:actual-asphr-protocol}, we describe and prove the security of Anysphere's real-world implementation. We focus on a technique we use called prioritization, which trades a small metadata leakage for efficiency.

%\todo{Currently, we assume all clients have registered before execution. We also do not handle trust establishment.}

%\todo{Also, CF attack is a huge problem! What should we do about it?}

\section{Conventions}
We use the following notational conventions.
\begin{itemize}
    \item When we write $f(\cdot)$, the dot might hide several variables.
    
    \item Given an oracle $O(x, \cdot)$ and a series $\{x_i\}$, define $O(\{x_i\}, \cdot)$ as the oracle whose input contains an extra argument $j$ and outputs $O(\{x_i\}_i, j, \arg) = O(x_j, \arg)$.

    \item Given a series $\{a_i\}$, and a set of indices $S$, let $a_S$ denote $\{a_i\}_{i \in S}$. 

    \item Experiments are always parametrized by the security parameter $\lambda$. When we say two experiments are indistinguishable, we mean the view of the adversary in the two experiments are indistinguishable. The view of the adversary consists of all inputs, outputs, and internal randomness of the adversary.
    
    \item When machines "return" in a method, they do not execute any subsequent commands and exit the method immediately.
\end{itemize}
